Won’t you be my neighboR?

### 2019-05-20 msu-workshop-2019.Rmd
update

  - [Doing data science with R](https://r4ds.had.co.nz/) by Wickham and
    Grolemund (2017)
  - [Big magic with R: Creating learning beyond
    fear](https://speakerdeck.com/apreshill/big-magic-with-r-creative-learning-beyond-fear)
    by Hill (2017)
  - [Data science in education](https://github.com/data-edu/data-science-in-education)

@@

>>>>

  - [Doing data science with R](https://r4ds.had.co.nz/) by Wickham and
    Grolemund (2017)
  - [Big magic with R: Creating learning beyond
    fear](https://speakerdeck.com/apreshill/big-magic-with-r-creative-learning-beyond-fear)
    by Hill (2017)
  - [Data science in education](https://github.com/data-edu/data-science-in-education)
  - [R Studio Community](https://community.rstudio.com/)

@@

# Useful packages

With one exception, can install via `install.packages(<name-of-package)`, i.e., `install.packages("tidylog").

- tidyverse: tools for data manipulation and processing
- tidylog: companion to the tidyverse; gives you feedback
- haven: import and export files for other statistical software
- apaTables: create APA-style tables in MS Word format
- devtools: to download packages only available on GitHub
- psych: general psychological science-related analysis tools
- skimr: quickly calculate summary statistics for a data frame
- lavaan: structural equation modeling
- tipyLPA: latent profile analysis
- lme4: multi-level modeling (HLM)
- sjstats: convenient statistical functions
- poLCA: latent class analysis
- rmarkdown: reports (PDF, Word, HTML, etc.)
- papaja: APA-style paper generation (must install from [GitHub](https://github.com/crsh/papaja))
- blogdown create a website/blog
- xaringan: create presentations
- MplusAutomation: Run Mplus via R

# People (and a few hashtags) to follow (on Twitter)

- [Jesse Mostipak](https://twitter.com/kierisi)
- [Alison Hill](https://twitter.com/apreshill)
- [Hadley Wickham](https://twitter.com/hadleywickham)
- [Daniel Anderson](https://twitter.com/datalorax_)
- [Mara Averick](https://twitter.com/dataandme)
- [Thomas Mock](https://twitter.com/thomas_mock)
- [Angela Li](https://twitter.com/CivicAngela)
- [R4DS community](https://twitter.com/R4DScommunity)
- [#tidytuesday](https://twitter.com/hashtag/TidyTuesday?src=hash)
- [#rstats](https://twitter.com/hashtag/rstats?src=hash)
- [David Robinson](https://twitter.com/drob)
- [Julia Silge](https://twitter.com/juliasilge)
- [Gabriela de Quieroz](https://twitter.com/gdequeiroz)
- [Joshua Rosenberg](https://twitter.com/jrosenberg6432)
- [Emily Bovee](https://twitter.com/ebovee09)
